\documentclass{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[usenames]{color}
\usepackage{fullpage}
\usepackage[hidelinks]{hyperref}
\usepackage{nopageno}

\leftmargin=0.25in
\oddsidemargin=0.25in
\textwidth=6.0in
\topmargin=-0.25in
\textheight=9.25in

\raggedright

\pagenumbering{arabic}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }



% DEFINITIONS

\newenvironment{changemargin}[2]{%
  \begin{list}{}{%
    \setlength{\topsep}{0pt}%
    \setlength{\leftmargin}{#1}%
    \setlength{\rightmargin}{#2}%
    \setlength{\listparindent}{\parindent}%
    \setlength{\itemindent}{\parindent}%
    \setlength{\parsep}{\parskip}%
  }%
  \item[]}{\end{list}
}

\newcommand{\lineover}{
  \begin{changemargin}{-0.05in}{-0.05in}
    \vspace*{-8pt}
    \hrulefill \\
    \vspace*{-2pt}
  \end{changemargin}
}

\newcommand{\header}[1]{
  \begin{changemargin}{-0.5in}{-0.5in}
    \scshape{#1}\\
  \lineover
  \end{changemargin}
}

\newcommand{\contact}[5]{
  \begin{changemargin}{-0.5in}{-0.5in}
    \begin{center}
      {\Large \scshape {#1}}\\ \smallskip
      {#2} | {#3}\\ \smallskip
      {#4} | {#5}\\ \smallskip
    \end{center}
  \end{changemargin}
}

\newenvironment{body} {
  \vspace*{-16pt}
  \begin{changemargin}{-0.25in}{-0.5in}
  }
  {\end{changemargin}
}

% END DEFINITIONS



\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Contact Info
\contact{Johnny Lee}
        {\href{mailto:itzfx2@gmail.com}{itzfx2@gmail.com}}
        {(626) 274-1140}
        {\href{https://www.linkedin.com/in/jlee1031}{linkedin.com/in/jlee1031}}
        {\href{https://github.com/itzfx}{github.com/itzfx}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Career
\header{Career History}

\begin{body}
  \vspace{14pt}
  \textbf{Software Engineer}, \emph{Yelp Inc.}, San Francisco, CA \hfill \emph{May 2012 - Present}\\
  \vspace*{-4pt}
  \begin{itemize} \itemsep -0pt  % reduce space between items

    \item Served as the project lead of a group of 4 engineers for the ``Message the Business'' feature.
    \begin{itemize} \itemsep -0pt
      \item Scoped the size of the project with the product manager and the technical lead.
      \item Designed the underlying schema for each part of the feature such as the MySQL database tables, the handling of asynchronous tasks using Gearman, and potential error states for users sending or replying to a message.
      \item Involved in creating methods to collect metrics about the use of the feature. These methods included use of MapReduce over access logs and designing complex but efficient SQL queries (queries were generated through an Object Relational Mapper).
      \item Designed and implemented the ``reply by email'' feature. This included multiple layers of security considerations since email is inherently insecure.
    \end{itemize}

    \item One of the primary developers working to convert the biz.yelp.com backend to be more service oriented.
    \begin{itemize} \itemsep -0pt
      \item Identified and moved pages and features on biz.yelp.com that could be most easily extracted from the existing monolith style codebase to the new backend service.
      \item Created runbooks that detailed the steps that need to be taken to move a feature from the monolith to the backend service for future developers.
    \end{itemize}

    \item One of the primary developers for ``Self-Serve Packaged Yelp Ads'' which allows business owners to purchase advertising along with other products, such as call tracking, at a discount.
    \begin{itemize} \itemsep -0pt
      \item Integrated the application of ``promotion codes'' during a purchase.
      \item Developed a method to measure servlet timings to compare the efficiency of the new servlets versus the old servlets for ``Self-Serve Yelp Ads''.
      \item Implemented tracking of users' progress through the purchase flow to measure conversions.
      \item Designed the data model for storing details about purchasable packages.
    \end{itemize}

    \item Took over responsibility of the ``Your Business On Yelp'' email newsletter backend.
    \begin{itemize} \itemsep -0pt
      \item The original engineers that were responsible for the feature left the company.
      \item Figured out and documented the workflow for making sure that the metrics shown to business owners were correct and generated on time for the newsletter.
    \end{itemize}

    \item Served as the project lead of a group of 4 engineers to redesign the Yelp Business Owner's site.
    \begin{itemize} \itemsep -0pt
      \item Completely updated the frontend of the Yelp Business Owner's site.
      \item Backend was updated to use Elastic Search to help business owners with multiple locations search for their locations quickly.
      \item Refactored legacy code that was causing bottlenecks in the response time for the new design. The bottleneck made the website unusably slow for the owners of some of the largest businesses.
    \end{itemize}

    \item One of the primary developers for the ``Call To Action'' button.
    \begin{itemize} \itemsep -0pt
      \item Designed and refined the underlying database schema.
      \item Created the business logic that determined whether a business qualified for the feature.
      \item Used MapReduce to extract metrics from log data.
    \end{itemize}

    \item Work involved using: Python, Javascript, Cheetah, Testify, pytest, Tron, MRJob, Git, etc...

  \end{itemize}

  \textbf {Software Engineer}, \emph{Global Aerospace Corp.}, Altadena, CA \hfill \emph{Oct 2009 - Dec 2012}\\
  \vspace*{-4pt}
  \begin{itemize} \itemsep -0pt
    \item Contributed to Dakota, a tool to simulate the performance of rechargeable lithium-ion batteries, and the framework for simulating complex real-world physics using object oriented programming methods.
    \item Identified mathematical problems in the first-principles model Dakota was based upon and implemented solutions given by the modeler.
    \item Used the Facade design pattern to create a complex object by reusing existing simple objects.
    \item Work involved using: Java, JUnit, Ant, SVN, etc...
  \end{itemize}
\end{body}

\smallskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
\header{Education}

\begin{body}
  \vspace{14pt}
  \textbf{B.A. Computer Science}, \emph{University of California}, Berkeley, CA \hfill \emph{Graduated: December 2012} \\
\end{body}

\smallskip


\end{document}
